\documentclass[10pt,a4paper]{article}

\usepackage[margin=1.3cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{setspace}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}
\titlespacing{\section}{0pt}{4pt}{2pt}
\setstretch{0.95}

\pagenumbering{gobble}

\begin{document}

\begin{center}
    {\LARGE \textbf{Martín Oscar Fourcans}} \\
    \vspace{2pt}
    Backend Developer \\
    \vspace{2pt}
    \href{mailto:ingfourcans@gmail.com}{ingfourcans@gmail.com} \quad | \quad 
    +54 381 4090457 \quad | \quad 
    \href{https://linkedin.com/in/ingfourcans}{linkedin.com/in/ingfourcans} \\
    Argentina (Remote)
\end{center}

\vspace{3pt}

\section*{Professional Summary}

Computer Engineer with 15 years of experience in analysis, design, and development of solutions mainly focused on process management and optimization within organizations.

Throughout my career, I have participated in the full project lifecycle, from functional definition to implementation and continuous improvement, combining technical expertise with business understanding.

Currently working as a backend developer, with experience in collaborative environments and technical decision-making. Seeking remote opportunities where I can contribute experience, commitment, and growth in dynamic environments.

\vspace{3pt}

\section*{Professional Experience}

\noindent{{\large \textbf{Backend Developer — Hexacta · Contract · Remote \hfill Feb 2025 - Present}}}\\[-3pt]
{\rule{\textwidth}{0.25pt}}
\begin{itemize}
    \item Design and development of RESTful APIs.
    \item Integration with external services (third-party APIs).
    \item Creation of endpoints (GET, POST, PUT, DELETE).
    \item Implementation of Clean Architecture.
\end{itemize}
\vspace{2pt}
{\small \textbf{Technologies:} C\#, .NET, Entity Framework Core, Bootstrap, SQL Server}

\vspace{3pt}

\noindent{{\large \textbf{Backend Developer — Andreani Group · Contract · Remote \hfill Oct 2021 - Dec 2024}}}\\[-3pt]
{\rule{\textwidth}{0.25pt}}
\begin{itemize}
    \item Design and development of RESTful APIs.
    \item Endpoint protection.
    \item Implementation of authentication and authorization mechanisms.
    \item Participation in key technology migrations: .NET Framework → .NET Core.
    \item Performance optimization and query tuning.
\end{itemize}
\vspace{2pt}
{\small \textbf{Technologies:} C\#, .NET, Entity Framework Core, JavaScript, Bootstrap, SQL Server}

\vspace{3pt}

\noindent{{\large \textbf{Backend Developer — Ministry of Education · On-site \hfill Nov 2012 - Sep 2021}}}\\[-3pt]
{\rule{\textwidth}{0.25pt}}
\begin{itemize}
    \item Developed and maintained web applications for large-scale educational information management, participating in projects related to student administration, human resources, and document management. Served as a technical reference.
    \item In later years, migrated legacy systems from VB and ASP to C\# ASP.NET Core.
    \item Contributed to solutions aimed at improving data availability for decision-making. Crystal Reports with SQL Server was used.
    \item Worked on the development and implementation of a web-based document management system using ASP, JavaScript, and SQL Server.
\end{itemize}
\vspace{2pt}
{\small \textbf{Technologies:} C\#, .NET, Dapper, ASP, JavaScript, Bootstrap, SQL Server}

\vspace{3pt}

\noindent{{\large \textbf{Backend Developer — Mediterraneo Transport Company · On-site \hfill Nov 2006 - Nov 2012}}}\\[-3pt]
{\rule{\textwidth}{0.25pt}}
\begin{itemize}
    \item Designed and developed from scratch the company's core management system, covering logistics, billing, and accounting processes using Visual Basic and SQL Server.
    \item Took full ownership of the product lifecycle, from functional definition to implementation and continuous evolution, including infrastructure management.
    \item The system became the central platform of the organization, improving operational efficiency and supporting reliable accounting management.
\end{itemize}
\vspace{2pt}
{\small \textbf{Technologies:} Visual Basic, SQL Server, Crystal Reports}

\vspace{3pt}

\section*{Education}

\textbf{Computer Engineering - Graduated} \\
UNSTA - Universidad del Norte Santo Tomas de Aquino \hfill 1998 – 2004 \\

\vspace{1pt}

\textbf{Master of Business Administration (MBA) - All coursework completed} \\
Universidad Nacional de Tucumán \hfill 2006 – 2012

\vspace{3pt}

\section*{Languages}

\textbf{Spanish - Native} \\

\vspace{1pt}

\textbf{English – B1 (Intermediate, currently improving)} \\

\end{document}